Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-03-28 NovelLBM.tex
shuffle error for different gamma dot
remove comment

As additional quantitative validation, we simulate a pure shear flow driven by imposing a fixed velocity at the top and bottom of the computational box and using periodic boundary conditions in the other two directions.
The box dimension is 2x43x2.
We use PTT with the methyl cellulose parameters and vary the shear rate to cover the full range starting from the zero-shear all the way to the infinite-shear plateau displayed in figure~\ref{fig:fit_mc} of the main text.
The shuffling is fixed at $\alpha_\text{s} = 1$ and the viscosity as function of shear rate is computed by dividing the total fluid stress at the center of the box by the shear rate.
Figure~\ref{fig:wiParameterStudy}~(a) shows that our simulations are in very good agreement with the semi-analytical solution with a maximum error of \num{2e-11}.
Importantly, we show in figure~\ref{fig:wiParameterStudy}~(b) that this very good agreement is independent of the shuffling parameter $\alpha_\text{s}$.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/wiParameterStudy.pdf}
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/suffleParameterStudy.pdf}
		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$. Shown at \SI{1}{\per\second} and .}
		\label{fig:wiParameterStudy}
	\end{figure}\todo{1e5; maybe write this in legend}

@@

		\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
		\caption{In planar Poiseuille flow, the result is near identical for different $\alpha_\text{s}$. The error reveals minor differences. Aside from the wall nodes, the largest error appears for small shuffle fractions. For large ones, the error appears to become independent of $\alpha_\text{s}$. This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself. This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers. \SG{ is this planar or cylindrical? }\RK{done}}
		\label{fig:ShuffleInPoiseuille}
	\end{figure}

>>>>

As additional quantitative validation, we simulate a pure shear flow driven by imposing a fixed velocity at the top and bottom of the computational box and using periodic boundary conditions in the other two directions.
The box dimension is 2x43x2.
We use PTT with the methyl cellulose parameters and vary the shear rate to cover the full range starting from the zero-shear all the way to the infinite-shear plateau displayed in figure~\ref{fig:fit_mc} of the main text.
The shuffling is fixed at $\alpha_\text{s} = 1$ and the viscosity as function of shear rate is computed by dividing the total fluid stress at the center of the box by the shear rate.
Figure~\ref{fig:wiParameterStudy}~(a) shows that our simulations are in very good agreement with the semi-analytical solution with a maximum error of \num{2e-11}.
Importantly, we show in figure~\ref{fig:wiParameterStudy}~(b) that this very good agreement is independent of the shuffling parameter $\alpha_\text{s}$.
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/wiParameterStudy.pdf}
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/suffleParameterStudy.pdf}
		\caption{(a) The local viscosity determined by a shear flow simulation is in very good agreement with the semi-analytical theory.
		(b) The error is negligibly small and independent of the shuffling parameter $\alpha_\text{s}$.}
		\label{fig:wiParameterStudy}
	\end{figure}

@@

		\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/ShuffleInPoiseuille.pdf}
		\caption{In planar Poiseuille flow, the result is near identical for different $\alpha_\text{s}$. The error reveals minor differences. Aside from the wall nodes, the largest error appears for small shuffle fractions. For large ones, the error appears to become independent of $\alpha_\text{s}$. This indicates, that the observed difference might be due to the Mach number changing for different $\alpha_\text{s}$ and not due to the shuffling itself. This is due lower $\alpha_\text{s}$ leading to lower LBM viscosities and such to higher Mach numbers.}
		\label{fig:ShuffleInPoiseuille}
	\end{figure}
